### 2023-03-30 resilience-safe-down.tex
up

\begin{theorem}\label{down-down}
The resilience problem is undecidable for WSTS with
%	with more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

\begin{proof}
In the case of a WSTS with at least two minimal elements $m_1$ and $m_2$, the problem of whether $m_2$ is reachable from $m_1$ reduces itself to the resilience problem, hence its undecidability.  
\mathieu{dévellopper un peu la preuve, $m_2$ minimal de $\Safe$, $m_1$ minimal de $\Bad$...}
\end{proof}

In the case of a WSTS with only one minimal element,  
% (ex: Petri Nets and their «Zero») 
then by downward closure the minimal element is present in both $\Safe$ and $\Bad$ and hence resilience always hold.

>>>>

\begin{theorem}\label{down-down}
The resilience problem is undecidable for strong effective WSTS with
%	with more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

\begin{proof}
Let us consider the case of a WSTS with at least two minimal elements $m_1$ and $m_2$.
The problem of whether $m_2$ is reachable from $m_1$ reduces itself to the resilience problem by considering $\Safe=\downarrow m_2 = \{ m_2\}$ and $\Bad=\downarrow m_1 = \{ m_1\}$. By undecidability of the reachability problem we conclude.  
\end{proof}

In the case of a WSTS with only one minimal element,  
then by downward closure the minimal element is present in both $\Safe$ and $\Bad$ which contradicts the assumption $\Safe \cap \Bad= \emptyset$.
